---
title: "Regession analysis report"
format: 
  html:
    number-sections: true
    number-depth: 4
editor: visual
code-fold: true
execute: 
  warning: false
  message: false
---

# Environment:

R version:

```{r}
R.version
```

Libraries:

```{r}
library(tidyverse)
library(fixest)
library(plm)
library(broom)
library(scales)
library(here)
```

Data:

```{r}
firm_table <- read_rds(here("01_DATA/APS/core_sample_assigned.rds"))

firm_table <- firm_table %>% 
  select(anio_fiscal,
         identificacion_informante_anon,
         group_assign,
         porcentaje_aps_pff,
         porcentaje_aps_ext) %>% 
  mutate(across(c(porcentaje_aps_pff,porcentaje_aps_ext),
                ~.x/100))
```

# Version 1: (T-Min + T-Maj) Treatment vs (C-Min + C-Maj) Control

## Dependent variable: Tax haven participation

### Level (Tax haven participation)

Data preparation:

```{r}

reg_table <- firm_table %>% 
  filter(group_assign %in% c("C-Min","C-Maj","T-Min","T-Maj")) %>% 
  mutate(
    post = as.numeric(anio_fiscal >= 2015),
    post = factor(post,levels = c(0,1), labels = c("Pre","Post")),
    treatment = as_factor(group_assign),
    treatment = fct_collapse(treatment,
                             Control = c("C-Min","C-Maj"),
                             Treatment = c("T-Min","T-Maj")),
    treatment = fct_relevel(treatment,c("Control","Treatment"))
  ) %>% 
  select(
    pff_p = porcentaje_aps_pff,
    post,
    treatment,
    anio_fiscal,
    firm_id = identificacion_informante_anon
  )

```

#### Model: with no fixed effects:

```{r}
model <- lm(data = reg_table,
            formula = pff_p ~ treatment + post + treatment:post)

conint <- tidy(model,
               conf.int = TRUE)

perfor <- glance(model)

coeftest(model)
```


```{r}
conint %>% 
  mutate(term = str_remove_all(term,"^treatment|^post"),
         term = str_replace(term,":post",":")) %>% 
  ggplot() +
  geom_point(aes(x = term, y = estimate)) +
  geom_text(aes(x = term, 
                y = estimate,
                label = round(estimate, 3)),
            vjust = -0.5,
                 color = "#841CD4") +
  geom_linerange(aes(x = term,
                     ymin = conf.low, 
                     ymax = conf.high ),
                 color = "#841CD4") +
  coord_flip() +
  theme_minimal() +
  theme(axis.title= element_blank()) +
  labs(title = "DiD Model with lm() function",
       subtitle = "pff_p ~ treatment + post + treatment:post")

summary(model)
```

#### Model: with firm and year fixed effects:

```{r}

fe_model <- feols(data = reg_table,
                  fml = pff_p ~ treatment + post + treatment:post,
                  index = c("anio_fiscal","firm_id"))

coefplot(fe_model)

summary(fe_model)

```

### Log(Tax haven participation)

Data preparation:

```{r}

reg_table <- reg_table %>% 
  mutate(lop_pff = log(((pff_p*100) + 1)/100))
```

#### Model: with no fixed effects:

```{r}

model <- lm(data = reg_table,
            formula = lop_pff ~ treatment + post + treatment:post)

coefplot(model)

summary(model)

```

#### Model: with firm and year fixed effects:

```{r}

fe_model <- feols(data = reg_table,
                  fml = lop_pff ~ treatment + post + treatment:post,
                  index = c("anio_fiscal","firm_id"))

coefplot(fe_model)

summary(fe_model)

```

### Relative to 2014 (Tax haven participation)

Data preparation:

```{r}
reg_2014 <- reg_table %>% 
  filter(anio_fiscal == 2014) %>% 
  select(firm_id,
         pff_2014 = pff_p)

reg_table <-reg_table %>% 
  left_join(reg_2014) %>% 
  mutate(pff_rel = if_else(
    pff_2014 == 0 | is.na(pff_2014), NA_real_, pff_p/pff_2014
    
  ))

```

#### Model: with no fixed effects:

```{r}

model <- lm(data = reg_table,
            formula = pff_rel ~ treatment + post + treatment:post)

coefplot(model)

summary(model)

```

#### Model: with firm and year fixed effects:

```{r}

fe_model <- feols(data = reg_table,
                  fml = pff_rel ~ treatment + post + treatment:post,
                  index = c("anio_fiscal","firm_id"))

coefplot(fe_model)

summary(fe_model)

```

## Dependent variable: Dominant participation in group

### Level (participation)

Data preparation:

```{r}

reg_table <- firm_table %>% 
  filter(group_assign %in% c("C-Min","C-Maj","T-Min","T-Maj")) %>% 
  mutate(
    post = as.numeric(anio_fiscal >= 2015),
    post = factor(post,levels = c(0,1), labels = c("Pre","Post")),
    treatment = as_factor(group_assign),
    treatment = fct_collapse(treatment,
                             Control = c("C-Min","C-Maj"),
                             treatment = c("T-Min","T-Maj")),
    participation = if_else(
      treatment == "Control", porcentaje_aps_ext,porcentaje_aps_pff
    )
  ) %>% 
  select(
    participation,
    post,
    treatment,
    anio_fiscal,
    firm_id = identificacion_informante_anon
  )

```

#### Model: with no fixed effects:

```{r}

model <- lm(data = reg_table,
            formula = participation ~ treatment + post + treatment:post)

coefplot(model)

summary(model)
```

#### Model: with firm and year fixed effects:

```{r}

fe_model <- feols(data = reg_table,
                  fml = participation ~ treatment + post + treatment:post,
                  index = c("anio_fiscal","firm_id"))

coefplot(fe_model)

summary(fe_model)

```

### Log(Tax haven participation)

Data preparation:

```{r}

reg_table <- reg_table %>% 
  mutate(lop_participation = log(((participation*100) + 1)/100))
```

#### Model: with no fixed effects:

```{r}

model <- lm(data = reg_table,
            formula = lop_participation ~ treatment + post + treatment:post)

coefplot(model)

summary(model)

```

#### Model: with firm and year fixed effects:

```{r}

fe_model <- feols(data = reg_table,
                  fml = lop_participation ~ treatment + post + treatment:post,
                  index = c("anio_fiscal","firm_id"))

coefplot(fe_model)

summary(fe_model)

```

### Relative to 2014 (Tax haven participation)

Data preparation:

```{r}
reg_2014 <- reg_table %>% 
  filter(anio_fiscal == 2014) %>% 
  select(firm_id,
         p_2014 = participation)

reg_table <-reg_table %>% 
  left_join(reg_2014) %>% 
  mutate(p_rel = if_else(
    p_2014 == 0 | is.na(p_2014), NA_real_, lop_participation/p_2014
    
  ))

```

#### Model: with no fixed effects:

```{r}

model <- lm(data = reg_table,
            formula = p_rel ~ treatment + post + treatment:post)

coefplot(model)

summary(model)

```

#### Model: with firm and year fixed effects:

```{r}

fe_model <- feols(data = reg_table,
                  fml = p_rel ~ treatment + post + treatment:post,
                  index = c("anio_fiscal","firm_id"))

coefplot(fe_model)

summary(fe_model)

```
